\section{Limitations \& Future Work}
\label{sec:future_work}

\textbf{Limitations of our implementation.} The accuracy of our implementation could be improved using the precomputed FGD instead of the Fresnel approximation. Additionally, we could implement using covariance matrices instead of two-component vectors for the variance in order to allow rotated tangent vector fields. For the isotropic case we could use the mentioned split sum approximation for image based lighting instead of the Monte Carlo integration which would result in higher efficiency and accuracy. The adjusted split sum approximation for the anisotropic case could also be integrated in our implementation. To improve energy conservation we could implement a scaling factor method or use a FGD texture accounting for multiple scattering.\\
\textbf{Limitations of the model.} For high roughness values of the layers the approximation accuracy decreases visually noticeable. Further, the model lacks to reproduce some color shifts at grazing angles, occurring because of total reflection. Another limitation is the restriction that all layers need to be GGX interfaces and that all interfaces need to be plane parallel. Additionally, as the GGX distribution is no longer circular at grazing angles, the approximation using a radially symmetric function to model the variance introduces inaccuracy. For the anisotropic model another limitation is, that diamond shaped highlights, occurring because of opposing anisotropies between two layers, can not be modeled with GGX lobes.

%

Two other limitations of the presented model had been already solved, as mentioned in Section \ref{sec:related_work}.

\noindent\textbf{Future Work.} Apart from finding solutions for the remaining limitations, it would be interesting to extend the model to be able to reproduce iridescence effects and to support glint layers.